Argennon: A Scalable Smart Contract Platform

### 2021-06-24 tex/sections/consensus.tex
Comment out a buggy part in the consensus
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

If the total online stake goes lower than \texttt{minOnlineStake} threshold, nodes initiate the recovery
consensus protocol.

As we mentioned before, every $m$ blocks of the Argennon blockchain needs a certificate from the committee
of validators. This means that assuming the last certified block by the validators is valid, for issuing the block
certificate, the committee needs to conditionally validate $m$ blocks. We call these $m$ blocks the
validation set. To reduce resource usage of validators' nodes, the protocol requires honest nodes to only
conditionally validate a subset of the validation set. Validators that have a stake lower than
average should only validate one block in expectation.

More precisely, to decide about signing the block certificate, a honest member of the validators'
committee iterates over every block of the validation set, and selects a block for validation with
probability $p_u$. In this way, a member of the validators' committee will select $p_{u}m$ blocks in expectation.
Then, the honest member conditionally validates the selected blocks. If the member has selected more than one block,
he may validate the selected blocks in parallel.
If all checked blocks are valid, the validator issues an "accept"
signature, otherwise he issues a "reject" signature.

>>>>

If the total online stake goes lower than \texttt{minOnlineStake} threshold, nodes initiate the recovery
consensus protocol.
%
%As we mentioned before, every $m$ blocks of the Argennon blockchain needs a certificate from the committee
%of validators. This means that assuming the last certified block by the validators is valid, for issuing the block
%certificate, the committee needs to conditionally validate $m$ blocks. We call these $m$ blocks the
%validation set. To reduce resource usage of validators' nodes, the protocol requires honest nodes to only
%conditionally validate a subset of the validation set. Validators that have a stake lower than
%average should only validate one block in expectation.
%
%More precisely, to decide about signing the block certificate, a honest member of the validators'
%committee iterates over every block of the validation set, and selects a block for validation with
%probability $p_u$. In this way, a member of the validators' committee will select $p_{u}m$ blocks in expectation.
%Then, the honest member conditionally validates the selected blocks. If the member has selected more than one block,
%he may validate the selected blocks in parallel.
%If all checked blocks are valid, the validator issues an "accept"
%signature, otherwise he issues a "reject" signature.

### 2021-06-24 tex/sections/elements.tex
Comment out a buggy part in the consensus
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Every Argennon transaction is required to specify a cap for all the resources it needs. This
will include memory, network and processor related resources. The protocol defines an execution cost for
every AVM instruction, reflecting the amount of resources its emulation needs, and every transaction is required
to specify a maximum execution cost. If during emulation, a transaction reaches this maximum cost, it will be
considered failed and the network can receive the proposed fee of that transaction.

@@

\note{An Argennon transaction always pays all of its proposed fee, no matter how much of its predefined resources
were not used in the final emulation. This will incentivize users to exactly report their
transactions resource usage.}

>>>>

Every Argennon transaction is required to specify a cap for all the resources it needs. This
includes memory, network and processor related resources. The protocol defines an execution cost for
every AVM instruction, reflecting the amount of resources its emulation needs, and every transaction is required
to specify a maximum execution cost. If during emulation, a transaction reaches this maximum cost, it will be
considered failed and the network can receive the proposed fee of that transaction.

@@

\subsection{Transaction Fee}\label{subsec:fee}

Every Argennon transaction is required to pay two types of fees: execution fee and storage fee. A transaction pays
its fees by providing digital signatures of one or more accounts authorizing the transfer of the amount of fee in
ARG from one or more accounts to the fee sink accounts.
\note{An Argennon transaction always pays all of its proposed fee, no matter how much of its predefined resources
were not used in the final emulation. This will incentivize users to report the resource usage of their
transactions more accurately.}
